---
title: 'Between Human Dignity and Security: Identifying Citizen and Elite Preferences
  and Concerns over Refugee Reception'
output: html_document
date: "2025-04-14"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Hello! 

Welcome to the R Code of the "Between Human Dignity and Security: Identifying Citizen
and Elite Preferences and Concerns over Refugee Reception" article.

This code takes about XX hours to run from top to bottom and replicates the following figures:
Figure_1, Figure_2, Figure_3, Figure_4, Figure_5, Figure_9, Figure_10, Figure_11, 
Figure_14
and Tables and Figures in Appendix A and B.

# Set-up 

Step 1. Creation of directory

The replicator should begin by inserting the path to the project folder they have created between the quotation marks. 

```{r set-path, include=FALSE}
directory <- "~/setyourowndirectory"
setwd(directory)
```

#Figure 1
```{r figure1}
source("Figure 1.R")
```

#Figure 2
```{r figure2}
source("Figure 2.R")
```

#Figure 3
```{r figure3}
source("Figure 3.R")
```

#Figure 4
```{r figure4}
source("Figure 4.R")
```

#Figure 5
```{r figure5}
source("Figure 5.R")
```

#Figures 9
```{r figure9}
source("Figure 9.R")
```

#Figures 10
```{r figure10}
source("Figure 10.R")
```

#Figures 11
```{r figure11}
source("Figure 11.R")
```

#Figures 14
```{r figure14}
source("Figure 14.R")
```

#Appendix
```{r Appendix}
source("Appendix_AandB.R")
```